---
title: "Coursera assignment"
subtitle: "Developing Data Products: A Shiny Application"
author: "Jacques Chatard"
date: "2019 june 11"
output:
  ioslides_presentation
---


<style>
body p {
  color: #141442;
}
slides > slide.title-slide hgroup h1 {  color: #35355b;
  font-size: 60px;
  letter-spacing: 10;
}
slides > slide.title-slide hgroup h2 {  
  color: #35355b;
  font-size: 30px;
  letter-spacing: 10;
}
h2 { 
 color: #2c3e5b; 		
}
h3 { 
 color: #2c3e5b;		
}
h2.title {
    color: #2c3e5b;
}
slides > slide.title-slide p {
  color: #2a3b56;
}

</style>


## Introduction  {.smaller}  

This application is about a very basic and very simple 'Shiny' application that wants to facilitate a naive visualization that can intuitively show the importance and possible influence of an **outlier value in a simple analysis of linear regression**.  

[Please click here to go to the application itself:](https://chatard.shinyapps.io/outliers/)  

[Please click here, to take a look at the code on Github:](https://github.com/chatard/Shyny_Outliers)  

### Structure of the application interface: 

The left part of the page is reserved for widgets from which we will enter the coordinates of an outlier.  

The right part of the screen includes **3 tabs**  reserved, in order:   

- 1 to display the plot.  

- 2 to a summary of the various influences of the outlier.    

- 3 and finally, a third tab' is reserved for an online help.    

 

## Our regression model:  {.smaller}  

we simulate a random distribution around a line according to the following model:
$\color{#394f77}{Y = \beta_0 + \beta_1 X + \epsilon}$
Where $\color{#394f77}{\beta_0}$ is the intercept,  $\color{#394f77}{\beta_1}$ is the slope and $\color{#394f77}{\epsilon}$ is a random background noise : $\color{#394f77}{\epsilon \sim \mathcal{N} (\mu , s)}$.  

So, I'm going to use a code like this :  

```{r model, echo=TRUE, eval=FALSE}
### <b>
noise <- rnorm(samplesize, noise.mean, noise.sd)
x <- 1:samplesize
y= slope*x + intercept + noise
### </b>
```

From left panel Shiny sliders I get x and y coordinates to **choose and fix the position of the outlier** which I finally add to vectors x and y like this:  

```{r addingoutlier, echo=TRUE, eval=FALSE}
### <b>
newx <- append(x, currentXoutlier, after = length(x))
newy <- append(y, currentYoutlier,  after = length(y))
### </b>
```

## Example: influence on the slope (1). {.smaller}        

```{r noise, results='asis'}
### <b>
samplesize = 42; x = 1: samplesize 
set.seed(112)
noise <- rnorm(samplesize, 7, 4)
y = 0.4*x + 4 + noise
md1 <- lm(y ~ x)
md1slope <- round(summary(md1)$coefficient[2,1], digits = 2)
# Now, I substitute a value ... (I add an outlier) . 
x[42] <- 98; y[42]<-105
md2<-lm(y~x)
md2slope <- round(summary(md2)$coefficient[2,1], digits = 2)
# looking how outlier influence the slope :    
paste0("slope without outlier = ", md1slope)
paste0("slop with an outlier =", md2slope )

### </b>

```

(1)This piece of code is similar to the one used in the **server.R** file of the Shiny application.

## Summary about parts of the ui: {.smaller}        

      


Sidebar panel:                   | Main panel (tabset panel): 
-------------------------------- | ---------------------------------
input slider for x coordinate    | **tabpanel "plot"**
-                                | (displays the interactive plot.) 
input slider for y coordtnate    | **tabpanel "summary"**
-                                | (displays results like slopes.)
input slider for sample size     | **tabpanel "help"**
-                                | (displays the use of the interface)
  
*The left panel contains the widgets needed to enter variables.*  
*The main panel is reserved for the output of the results.*



